---
title: "Comparison with Markus Werner"
author: "Martin Ueding"
date: "\\today"
output: pdf_document
---

In this notebook we compare the data from the new projection code with the
results that Markus Werner has generated with his code.

Markus has already projected all the data for the $\rho$ channel, we can just
use this to compare. His data is not only in a different format but also uses
different parametrizations for individual momenta $p_i$ via his $P'$ and $q'$
values.

We want to do a fully automated complete comparison such that there are no
manual steps which are additional sources of errors.

We have picked the B35.32 ensemble for no particular reason. From Markus we
take the contractions for configuration 2552 in the form of HDF5 files. Also we
take his projected correlators in the form of TSV files to compare to.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
library(paramvalf)
library(tibble)

debug_mode = TRUE
```

```{r}
total_momentum_ref <- function (total_momentum_sq) {
  if (total_momentum_sq == 0)
    c(0, 0, 0)
  else if (total_momentum_sq == 1)
    c(0, 0, 1)
  else if (total_momentum_sq == 2)
    c(1, 1, 0)
  else if (total_momentum_sq == 3)
    c(1, 1, 1)
  else if (total_momentum_sq == 4)
    c(0, 0, 2)
}

momentum_to_string <- function (momentum) {
  paste0(sprintf("%d", momentum), collapse = '')
}

total_momentum_str_to_vec <- function (total_momentum_str) {
  parts <- stringr::str_match(total_momentum_str, '(-?\\d)(-?\\d)(-?\\d)')
  sapply(parts[1, 2:4], as.integer)
}
```

This comparison will use paramvalf within a single notebook. Users of it might miss the `pv_load` and `pv_save` calls but we are just using it as a library and not as a fully fleged framework here.

The data resides in the “work” directory where as the working directory of this notebook is the source directory. Therefore we first need to find it. This is different on the various machines, so we will just try a few candidates.

```{r}
workdir_candidates <- c(
  '~/Lattice/NG2',
  '~/NG2'
)

for (path in workdir_candidates) {
  if (dir.exists(path)) {
    workdir <- path
    break
  }
}
```

# Reading actual data

We will do all the comparisons to the total momenta and irreps that we have projected. For this we just parse all the files for a selected configuration and build a parameter table out of them.

```{r}
split_filename <- function (path) {
  filename <- basename(path)
  parts <- stringr::str_match(filename, 'resolved_(.*)_(.*)_(.*)\\.js')
  parts[1, 2:4]
}

all_projected_paths <- Sys.glob(paste0(workdir, '/projected/resolved_*_*_2552.js'))

parts <- do.call(rbind, lapply(all_projected_paths, split_filename))
colnames(parts) <- c('total_momentum_str', 'irrep', 'config_number')
df <- as_tibble(parts)
df$path <- all_projected_paths
df$config_number <- as.integer(df$config_number)

irreps <- df_to_paramval(df, c('total_momentum_str', 'irrep', 'config_number'))
```

The parameter is the total momentum as string, we need to extract it as a three-vector and and also as a compute the $\vec P^2$.

```{r}
.func <- function (param, value) {
  total_momentum_vec <- total_momentum_str_to_vec(param$total_momentum_str)
  total_momentum_sq <- sum(total_momentum_vec^2)
  
  list(
    total_momentum_vec = total_momentum_vec,
    total_momentum_sq = total_momentum_sq)
}

total_momentum <- pv_call(.func, irreps)
```

For each irrep we need to figure out which relative momenta $q$ we actually have in our data. In case that there are no relative momenta available we have no coupling and therefore we can discard it.

```{r}
.func <- function (param, value) {
  data <- jsonlite::read_json(value$path)
  # TODO
  #irrep_col <- if (param$irrep == 'T1u') '2' else '1'
  irrep_col <- '1'
  q_avail_actual <- names(data[[param$total_momentum_str]][[param$irrep]][[irrep_col]][['1']])
  
  if (length(q_avail_actual) == 0) {
    return (NA)
  }
  
  list(actual_avail = q_avail_actual)
}

actual_avail <- pv_call(.func, irreps, total_momentum)
```

# Reading target data

Markus' parametrization works as
$$ p_1 = \frac{P'}{2} + q' \,, \quad p_2 = \frac{P'}{2} - q' \,. $$

The parametrization used in this code here is $p_1 = P - q$ and $p_2 = q$ for
the case of two particles. This means that in order to convert his
parametrization into mine one has to use the relations
$$ P = P' \,, \quad q = \frac{P'}{2} - q' \,. $$

The other way around works exactly the same:
$$ P' = P \,, \quad q' = \frac{P}{2} - q \,. $$

His correlator matrix format contains files called `operator-indices` that give
the three-vector $P$ that is actually used for that particular moving frame, as
well as the irrep row:

```
id	p_x	p_y	p_z	alpha
0	-1	0	0	1
1	0	-1	0	1
2	0	0	-1	1
3	0	0	1	1
4	0	1	0	1
5	1	0	0	1
```

One has to look up our $P$ and then find out the *operator id* from this table.

The correlator matrix elements are then labeled by their $q'_\text{source}$ and
$q'_\text{sink}$ values. These also correspond to indices that have to be read
off from the lines with the correct Dirac structure, `g: \gamma_{5},
\gamma_{5}`, in the file `gevp-indices`:

```
id	element
0	p: 1, g: \gamma_{50i}
1	p: 1, g: \gamma_{i}
2	p: 1, q: (0.0, 0.0, 0.5), g: \gamma_{5}, \gamma_{5}
3	p: 1, q: (0.0, 0.0, 1.5), g: \gamma_{5}, \gamma_{5}
4	p: 1, q: (1.0, 0.0, 0.5), g: \gamma_{5}, \gamma_{5}
5	p: 1, q: (1.0, 1.0, 0.5), g: \gamma_{5}, \gamma_{5}
```

From this we can deduce which correlator matrix rows and columns correspond to
my $q_\text{source}$ and $q_\text{sink}$. The following function allows us to convert Markus format into my format. This way the comparison will work with my parametrization.

```{r}
parse_markus_gevp_indices <- function (line) {
  pattern <- 'p: (\\d+), q: \\(([\\d.]+), ([\\d.]+), ([\\d.]+)\\), g: \\\\gamma_\\{5\\}, \\\\gamma_\\{5\\}'
  match <- stringr::str_match(line, pattern)
  total_momentum_sq <- as.numeric(match[1, 2])
  
  if (is.na(total_momentum_sq)) {
    return (NA)
  }
  
  relative_momenta_markus <- as.numeric(match[1, 3:5])
  
  total_momentum_vec <- total_momentum_ref(total_momentum_sq)
  relative_momenta_martin <- round(total_momentum_vec / 2 - relative_momenta_markus)
  
  momentum_to_string(relative_momenta_martin)
}

stopifnot('-1-10' == parse_markus_gevp_indices('p: 1, q: (1.0, 1.0, 0.5), g: \\gamma_{5}, \\gamma_{5}'))
stopifnot('000' == parse_markus_gevp_indices('p: 1, q: (0.0, 0.0, 0.5), g: \\gamma_{5}, \\gamma_{5}'))
stopifnot('00-1' == parse_markus_gevp_indices('p: 1, q: (0.0, 0.0, 1.5), g: \\gamma_{5}, \\gamma_{5}'))
stopifnot(is.na(parse_markus_gevp_indices('p: 1, g: \\gamma_{5}')))
```

We gather the number of correlator matrices that Markus has.

```{r}
glob <- sprintf('%s/reference/rho_p?_*_operator-indices.tsv', workdir)
target_filenames <- Sys.glob(glob)
```

For the correlator matrices that we have available in the actual data we also try to load the target data. They might not all exist as Markus has only created the files for the one that actually have coupling. In case the files do not exist we can therefore safely skip them.

```{r}
.func <- function (param, value) {
  operator_indices_path <- sprintf('%s/reference/rho_p%d_%s_operator-indices.tsv', workdir, value$total_momentum_sq, param$irrep)
  if (!file.exists(operator_indices_path)) {
    return (NA)
  }
  operator_indices <- read.table(operator_indices_path, sep = '\t', header = TRUE)
  
  filtered <- operator_indices %>%
    filter(p_x == value$total_momentum_vec[1],
           p_y == value$total_momentum_vec[2],
           p_z == value$total_momentum_vec[3],
           alpha == 1) %>%
    select(id, alpha)
  operator_id <- filtered$id
  
  gevp_indices_path <- sprintf('%s/reference/rho_p%d_%s_gevp-indices.tsv', workdir, value$total_momentum_sq, param$irrep)
  
  gevp_indices <- read.table(gevp_indices_path, sep = '\t', header = TRUE, stringsAsFactors = FALSE)
  
  target_gevp_indices_converted <- gevp_indices %>%
    mutate(relative_momenta = sapply(element, parse_markus_gevp_indices)) %>%
    filter(!is.na(relative_momenta)) %>%
    select(id, relative_momenta)
  
  list(target_gevp_indices = target_gevp_indices_converted,
       target_operator_id = filtered)
}

target_avail <- pv_call(.func, irreps, total_momentum)
```

# Matching up available and actual

## Number of correlator matrices

There is no notational difference in the total momentum and the irreps. We must be able to load all of Markus's correlator matrices. If we cannot do that, something is off. In case that the actual data contains more than the target data we do not have a problem because these are just the ones that Markus did not write out due to non-coupling.

The following table lists all the correlator matrices that were found in both target and actual data sets.

```{r}
semi_join(actual_avail$param, target_avail$param)
```

The following table lists the correlator matrices that show coupling in the actual data but are not available in the target data. This can either be errors while loading the target data or just that Markus deemed them irrelevant for $l = 1$ and $I_3 = 1$ scattering. It seems that all these ones are understood and therefore everything that not matched up is not a problem.

```{r}
anti_join(actual_avail$param, target_avail$param)
```

In the other direction there must be no target data sets which we do not have in the actual data set. The following table should have zero rows.

```{r}
anti_join(target_avail$param, actual_avail$param)
```

## Momenta orbits

Markus and I have chosen different representatives for the relative momenta from each orbit. This means that at first glance there are many correlator matrix elements just missing in the other data. One must use a list of relative momenta from the orbits in order to match this up. Using Mathematica we can create a mapping from relative momentum labels to their respective orbit representative.

```{r}
path <- sprintf('%s/momenta_orbits.js', workdir)
momentum_orbits <- jsonlite::read_json(path)
```

```{r}
.func <- function (param, value) {
  target_relative_momenta <- as.character(momentum_orbits[[param$total_momentum_str]][value$target_gevp_indices$relative_momenta])
  stopifnot(length(value$target_gevp_indices$relative_momenta) == length(target_relative_momenta))
  
  df <- tibble(
    target_gevp_id = value$target_gevp_indices$id,
    target_relative_momenta = target_relative_momenta)
  
  df2 <- df %>%
    filter(target_relative_momenta %in% value$actual_avail)
  
  if (nrow(df) != nrow(df2)) {
    str(param)
    cat(sprintf('%d -> %d\n', nrow(df), nrow(df2)))
    str(anti_join(df, df2))
    print(value$actual_avail)
  }
  
  if (nrow(df2) == 0) {
    return (NA)
  }
  
  i <- 1:nrow(df2)
  
  stopifnot('target_gevp_id' %in% colnames(df))
  stopifnot('target_relative_momenta' %in% colnames(df))
  
  grid <- as_tibble(expand.grid(i = i, j = i))
  attr(grid, 'out.attrs') <- NULL
  grid$target_source_id <- df$target_gevp_id[grid$i]
  grid$target_sink_id <- df$target_gevp_id[grid$j]
  grid$source_relative_momenta <- df$target_relative_momenta[grid$i]
  grid$sink_relative_momenta <- df$target_relative_momenta[grid$j]
  grid$i <- NULL
  grid$j <- NULL
  
  stopifnot(all(!is.na(grid$target_source_id)))
  stopifnot(all(!is.na(grid$target_sink_id)))
  
  list(matched_up_grid = grid)
}

matched_up <- pv_call(.func, actual_avail, target_avail)
```

During the process we might lose some of the data sets. The following table lists all the ones that got lost. This must not happen as it is an indication that there is no overlap in the relative momenta that are available. This likely means that either the momenta cutoffs are too strict in the new analytic projection code or that the correspondence using the momentum orbits has not worked correctly. All these cases must be understood and fixed.

```{r}
anti_join(target_avail$param, matched_up$param)
```

# Reading target correlators

At this point we have figured out the correspondence of operators. We can just take the outer product of these operators to flesh out the whole correlator matrix and load the elements from both the target and actual data.

```{r}
load_target_config <- function (path, config_number) {
  target <- read.table(path, header = TRUE)
  
  target_single <- dplyr::filter(target, cnfg == config_number)
  target_single$value
}

.func <- function (param, value) {
  stopifnot(nrow(value$target_operator_id) == 1)
  
  grid <- value$matched_up_grid
  
  grid$filename_target <- sprintf(
    '%s/reference/rho_p%d_%s_op%d_gevp%d.%d.tsv',
    workdir,
    value$total_momentum_sq,
    param$irrep,
    value$target_operator_id$id,
    grid$target_source_id,
    grid$target_sink_id)
  
  target_loaded <- lapply(grid$filename_target, load_target_config, config_number = param$config_number)
  grid$target <- target_loaded
  
  filename_actual <- value$path
  resolved <- jsonlite::read_json(filename_actual)
  load_actual_config <- function (q_source, q_sink) {
    irrep_col <- if (param$irrep %in% c('T1u')) '3' else '1'
    data <- unlist(resolved[[param$total_momentum_str]][[param$irrep]][[irrep_col]][['1']][[q_source]][[q_sink]])
    stopifnot(!is.null(data))
    return (data)
  }
  actual_loaded <- mapply(load_actual_config, grid$source_relative_momenta, grid$sink_relative_momenta, SIMPLIFY = FALSE, USE.NAMES = FALSE)
  grid$actual <- actual_loaded
  
  grid$time <- lapply(1:nrow(grid), function (i) 0:(length(grid$target[[1]])-1))
                        
  list(filename_actual = filename_actual,
       grid = grid)
}

loaded <- pv_call(.func, matched_up, total_momentum, target_avail, irreps)
```

# Comparison

For a comparison with the ggplot library it is easiest to convert the correlator matrices into the long format and have target and actual data in the same column instead of two distinct ones.

```{r}
.func <- function (param, value) {
  long <- tidyr::unnest(value$grid)
  long2 <- tidyr::gather(long, kind, correlator, target, actual)
  
  list(loaded_long = long2)
}

loaded_long <- pv_call(.func, loaded)
```

In the following we produce one comparison plot per correlator matrix, showing all the elements that could be matched up.

```{r}
.func <- function (param, value) {
  p <- ggplot(value$loaded_long, aes(x = time, y = abs(correlator), color = kind)) +
    geom_point(position = position_dodge(width = 0.3)) +
    scale_y_log10() +
    facet_grid(source_relative_momenta ~ sink_relative_momenta) +
    labs(title = "Comparison between Martin's and Markus's projection code",
         subtitle = sprintf('P = %s, irrep = %s, cnfg = %d', param$total_momentum_str, param$irrep, param$config_number),
         x = 't',
         y = expression(abs(C(t))),
         color = 'Data')
  
  path <- sprintf('%s/comparison', workdir)
  if (!dir.exists(path)) {
    dir.create(path)
  }
  ggsave(sprintf('%s/comparison-%s-%s.pdf', path, param$total_momentum_str, param$irrep), p, width = 10, height = 10)
  
  print(p)
  
  list()
}

pv_call(.func, loaded_long)
```

